Transfer learning for \'echelle spectroscopy with \texttt{blas\'e}

### 2022-03-03 paper/paper1/ms.tex
Figures are looking good now
Ok, finally settled on using WASP 69 as the demo source.

\begin{figure}[hbt!]
    \centering
    \includegraphics[width=0.8\textwidth]{figures/blase_clone_demo.png}
    \caption{PHOENIX spectrum cloned with blas\'e.  This $T_{\mathrm{eff}}=4100\;$K,  $\log{g}=3.5$ solar metallicity model has 11,759 individual cloned spectral lines, each with 3 tuned parameters.  The pictured 25 \AA~ chunk contains 73 spectral lines and represents a mere $<0.7\%$ portion of the entire spectral bandwidth that was cloned.  Some flaws can be seen near the cores of deep lines, or wings of broad lines.}
    \label{fig_cloned_spectrum_demo}
\end{figure}

@@

We compute the residual $\mathsf{R}(\bm{\lambda}_s)$ of native PHOENIX minus cloned model, illustrated in the bottom panel of Figure \ref{fig_cloned_spectrum_demo}\authorcomment1{make this figure!}. We see an RMS of $\blackout{1}\%$ residuals at native resolution, with a long tail of residuals up to $\blackout{20}\%$. The greatest residuals surround the deepest and broadest lines---such as Hydrogen and neutral alkali metal lines---for which the non-Voigt lineshapes stand out. Figure \ref{fig_poor_cloning_performance}\authorcomment1{make this figure} zooms in on the \censor{XX} line at $\censor{10200}\;$\AA.

\begin{figure}[hbt!]
    \centering
    \includegraphics[width=0.8\textwidth]{figures/blase_clone_demo_zoom.png}
    \caption{A zoom in of the region between the vertical gray bars in Figure \ref{fig_cloned_spectrum_demo}. There are 9 spectral lines in this view.}
    \label{fig_poor_cloning_performance}
\end{figure}

@@

\subsection{Line data clustering and conspicuous flaws}
We see some narrow lines devolve into missing continuum opacity, the favored tradeoff when the continuum estimate's poor performance outweighs the pain of a narrow-but-tolerably-small spike. This problem can be seen in Figure \ref{fig_poor_cloning_performance} where a line initialized at $\censor{10210}\;$\AA~ with an amplitude of ZZ and width of YY bloats to \censor{some other value}. These devolved lines tend to appear at poorly imitated broad-and-deep line wings. One can mitigate these devolved lines by adding more flexibility to the continuum or supporting more advanced line shapes.

>>>>

\begin{figure}[hbt!]
    \centering
    \includegraphics[width=0.8\textwidth]{figures/blase_clone_demo.png}
    \caption{PHOENIX spectrum cloned with blas\'e.  This $T_{\mathrm{eff}}=4700\;$K,  $\log{g}=4.5$ solar metallicity model has 9,028 individual cloned spectral lines, each with 3 tuned parameters.  The pictured 50 \AA~ chunk contains 121 spectral lines and represents about 1$\%$ of the entire spectral bandwidth that was cloned.  Some flaws can be seen near the cores of deep lines, or wings of broad lines.}
    \label{fig_cloned_spectrum_demo}
\end{figure}

@@

We compute the residual $\mathsf{R}(\bm{\lambda}_s)$ of native PHOENIX minus cloned model, illustrated in the bottom panel of Figure \ref{fig_cloned_spectrum_demo}\authorcomment1{make this figure!}. We see an RMS of $\blackout{1}\%$ residuals at native resolution, with a long tail of residuals up to $\blackout{20}\%$. The greatest residuals surround the deepest and broadest lines---such as Hydrogen and neutral alkali metal lines---for which the non-Voigt lineshapes stand out. Figure \ref{fig_zoom_cloning_performance}\authorcomment1{make this figure} zooms in on the \censor{XX} line at $\censor{10200}\;$\AA.

\begin{figure}[hbt!]
    \centering
    \includegraphics[width=0.8\textwidth]{figures/blase_clone_demo_zoom.png}
    \caption{Zoom in of the region between the vertical gray bars in Figure \ref{fig_cloned_spectrum_demo}. The cloned model has 7 spectral lines describing the 400 pixels in this 4 \AA~ chunk.  The native PHOENIX pixel sampling can be see as the boxy steps in both the native and cloned model.  }
    \label{fig_zoom_cloning_performance}
\end{figure}

@@

\subsection{Line data clustering and conspicuous flaws}
We see some narrow lines devolve into missing continuum opacity, the favored tradeoff when the continuum estimate's poor performance outweighs the pain of a narrow-but-tolerably-small spike. This problem can be seen in Figure \ref{fig_zoom_cloning_performance} where a line initialized at $\censor{10210}\;$\AA~ with an amplitude of ZZ and width of YY bloats to \censor{some other value}. These devolved lines tend to appear at poorly imitated broad-and-deep line wings. One can mitigate these devolved lines by adding more flexibility to the continuum or supporting more advanced line shapes.
